Delone lattice studies in \CIII, the space of three complex variables

### 2023-06-14 C3/C3.tex
responses to the reviewers' comment 2023-06-12

\documentclass[]{iucr}              % DO NOT DELETE THIS LINE
\usepackage{amssymb}
\usepackage[fleqn]{amsmath}
%\usepackage{bm}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{booktabs}
%\usepackage{calligra}
\usepackage{array}
\DeclareMathAlphabet{\mathcalligra}{T1}{calligra}{m}{n}
\def\mathbi#1{\textbf{\em #1}}
\numberwithin{equation}{section}
%\DeclareMathSymbol{\Gamma}{\mathalpha}{letters}{"00}
%\DeclareMathSymbol{\Lambda}{\mathalpha}{letters}{"03}
%\DeclareMathSymbol{\Omega}{\mathalpha}{letters}{"0A}
%\DeclareMathAlphabet{\mathitbf}{OML}{cmm}{b}{it}
\hyphenation{Niggli}
\def\mathbi#1{\textbf{\em #1}}
%\numberwithin{equation}{section}
%\DeclareMathSymbol{\Gamma}{\mathalpha}{letters}{"00}
%\DeclareMathSymbol{\Lambda}{\mathalpha}{letters}{"03}
%\DeclareMathSymbol{\Omega}{\mathalpha}{letters}{"0A}
%\DeclareMathAlphabet{\mathitbf}{OML}{cmm}{b}{it}
\usepackage{color}
\usepackage{ulem}
\usepackage{url}
\usepackage{yfonts}
%\usepackage{xr-hyper}
%\usepackage[draft]{hyperref}
%\usepackage{bibentry}
\newcommand{\SVI}[0]{$\bf{S^{6}}$}
\newcommand{\GVI}[0]{$\bf{G^{6}}$}
\newcommand{\CIII}[0]{$\bf{C^{3}}$}
\newcommand{\DVII}[0]{$\bf{D^{7}}$}
\newcommand{\VVII}[0]{$\bf{V^{7}}$}

@@

@@

	$\begin{bmatrix}
		\Minus{}_i	& 0					& 0 \\
		\Plus{}_i	&  \textrm{i}\Real{}	& \Real{} \\
		\Plus{}_i	& \textrm{i}\Imaginary{}	& \Imaginary{}
	\end{bmatrix}$
	%
	$\begin{bmatrix}
		\Minus{}_i	& 0					& 0 \\
		\Plus{}_i	& \textrm{i}\Imaginary{}	& \Imaginary{} \\
		\Plus{}_i	&  \textrm{i}\Real{}	& \Imaginary{} \\
	\end{bmatrix}$ 
	%
	$\begin{bmatrix}
		\Minus{}_i	& 0			& 0 \\
		\Plus{}_i	&  \Real{}	& \textrm{i}\Real{} \\
		\Plus{}_i	& \Imaginary{}		& \textrm{i}\Imaginary{}
	\end{bmatrix}	$
	%
	$\begin{bmatrix}
		\Minus{}_i	& 0		& 0 \\
		\Plus{}_i	& \Imaginary{}	& \textrm{i}\Imaginary{} \\
		\Plus{}_i	&  \Real{}& \textrm{i}\Imaginary{} \\
	\end{bmatrix}$ \\

@@

		\textrm{i}\Real{}	& \Plus{}_r		& \Real{} \\
		0				& \Minus{}_r	& 0 \\
		\textrm{i}\Imaginary{}	& \Plus{}_r		& \Imaginary{}
	\end{bmatrix}$
	%
	$\begin{bmatrix}
		\textrm{i}\Imaginary{}	& \Plus{}_r		&  \Imaginary{} \\
		0				& \Minus{}_r	& 0 \\
		\textrm{i}\Real{}	& \Plus{}_r		& \Real{} \\
	\end{bmatrix}$ e
	%
	$\begin{bmatrix}
		\Real{}	&\Plus{}_r		&   \textrm{i}\Real{} \\
		0		& \Minus{}_r	&  0 \\
		\Imaginary{}	&\Plus{}_r		& \textrm{i}\Imaginary{}
	\end{bmatrix}	$ 
	%
	$\begin{bmatrix}
		\Imaginary{}	& \Plus{}_r	& \textrm{i}\Imaginary{} \\
		0		&\Minus{}_r	&  0 \\
		\Real{}	& \Plus{}_r	&  \textrm{i}\Real{} \\
	\end{bmatrix}$ \\

@@

	$\begin{bmatrix}
		\textrm{i}\Real{}	& \Plus{}_i		& \Real{} \\
		0				& \Minus{}_i	& 0 \\
		\textrm{i}\Imaginary{}	& \Plus{}_i		& \Imaginary{}
	\end{bmatrix}$
	%
	$\begin{bmatrix}
		\textrm{i}\Imaginary{}	& \Plus{}_i		&  \Imaginary{} \\
		0				& \Minus{}_i	& 0 \\
		\textrm{i}\Real{}	& \Plus{}_ri	& \Real{} \\
	\end{bmatrix}$ 
	%
	$\begin{bmatrix}
		\Real{}	&\Plus{}_i		&   \textrm{i}\Real{} \\
		0		& \Minus{}_i	&  0 \\
		\Imaginary{}	&\Plus{}_i		& \textrm{i}\Imaginary{}
	\end{bmatrix}	$ 
	%
	$\begin{bmatrix}
		\Imaginary{}	& \Plus{}_i	& \textrm{i}\Imaginary{} \\
		0		&\Minus{}_i	&  0 \\
		\Real{}	& \Plus{}_i	&  \textrm{i}\Real{} \\
	\end{bmatrix}$ \\

@@

@@

The matrix multiply can be implemented as follows"

\begin{verbatim}
C3 C3::c3_s1(const C3& a) {
    C3 c;
    c[0] = c3_Minus_Real(a[0]);
    c[1] = c3_Plus_Real(a[0]) + c3_Real(a[1]) +
        c3_I_Times_Real(a[2]);
    c[2] = c3_Plus_Real(a[0]) + c3_Imag(a[1]) +
        c3_I_Times_Imag(a[2]);
    return c;
}
\end{verbatim}

Therefore, RedMat = \\
\begin{center}
	$\begin{bmatrix}
	\Minus{}_r	& 0			& 0 \\
	\Plus{}_r	&  \Real{}	& \textrm{i}\Real{} \\
	\Plus{}_r	& \Imaginary{}		&\textrm{i}\Imaginary{}
\end{bmatrix}	$
\end{center}

@@

\begin{center}
\{(-1.000,1.000) (4.000,6.000) (5.000,7.000)\} =\\
$\begin{bmatrix}
	\Minus{}_r	& 0			& 0 \\
	\Plus{}_r	&  \Real{}	& \textrm{i}\Real{} \\
	\Plus{}_r	& \Imaginary{}		&\textrm{i}\Imaginary{}
\end{bmatrix}	$
$\begin{Bmatrix}
	(1,2)\\
	(3,4)\\
	(5,6)
\end{Bmatrix}$\\

@@

	The identity in \CIII{} can also be written:\\

	$\bf{c'}$  = 
	$\begin{bmatrix}
		$1$	& $0$						&  $0$ \\
		$0$	& \Real{} +\textrm{i}\Imaginary{}	& $0$ \\
		$0$	& $0$						& \Real{} +\textrm{i}\Imaginary{} \\
	\end{bmatrix}$ 
	$\bf{c}$.
	\\

@@

\begin{figure}
	\includegraphics[width=1.0\textwidth]{19_57}
	label{19\_57}
	\caption{The PLA2 unit cells, Niggli-reduced, and five copies were perturbed 10\%
		orthogonally to \SVI{} vector, followed by Niggli reduction.}
\end{figure}

>>>>

\documentclass[preprint]{iucr}              % DO NOT DELETE THIS LINE
\usepackage{amssymb}
\usepackage[fleqn]{amsmath}
%\usepackage{bm}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{booktabs}
%\usepackage{calligra}
\usepackage{array}
\DeclareMathAlphabet{\mathcalligra}{T1}{calligra}{m}{n}
\def\mathbi#1{\textbf{\em #1}}
\numberwithin{equation}{section}
%\DeclareMathSymbol{\Gamma}{\mathalpha}{letters}{"00}
%\DeclareMathSymbol{\Lambda}{\mathalpha}{letters}{"03}
%\DeclareMathSymbol{\Omega}{\mathalpha}{letters}{"0A}
%\DeclareMathAlphabet{\mathitbf}{OML}{cmm}{b}{it}
\hyphenation{Niggli}
\def\mathbi#1{\textbf{\em #1}}
%\numberwithin{equation}{section}
%\DeclareMathSymbol{\Gamma}{\mathalpha}{letters}{"00}
%\DeclareMathSymbol{\Lambda}{\mathalpha}{letters}{"03}
%\DeclareMathSymbol{\Omega}{\mathalpha}{letters}{"0A}
%\DeclareMathAlphabet{\mathitbf}{OML}{cmm}{b}{it}
\usepackage{color}
\usepackage{ulem}
\usepackage{url}
\usepackage{yfonts}
%\usepackage{xr-hyper}
%\usepackage[draft]{hyperref}
%\usepackage{bibentry}
\newcommand{\SVI}[0]{$\bf{S^{6}}$}
\newcommand{\GVI}[0]{$\bf{G^{6}}$}
\newcommand{\CIII}[0]{$\bf{C^{3}}$}
\newcommand{\DVII}[0]{$\bf{D^{7}}$}
\newcommand{\VVII}[0]{$\bf{V^{7}}$}

@@

	The C3 vector transformations are represented as multiplication by a matrix of the operators defined in Table 1. When a complex vector component is 'multiplied' by an operator, the result is as defined in the table."

@@

	$\begin{bmatrix}
		\Minus{}_i	& 0					& 0 \\
		\Plus{}_i	&  \textrm{i}\Real{}	& \Real{} \\
		\Plus{}_i	& \textrm{i}\Imaginary{}	& \Imaginary{}
	\end{bmatrix}$
	%
	$\begin{bmatrix}
		\Minus{}_i	& 0					& 0 \\
		\Plus{}_i	& \textrm{i}\Imaginary{}	& \Imaginary{} \\
		\Plus{}_i	&  \textrm{i}\Real{}	& \Real{} \\
	\end{bmatrix}$ 
	%
	$\begin{bmatrix}
		\Minus{}_i	& 0			& 0 \\
		\Plus{}_i	&  \Real{}	& \textrm{i}\Real{} \\
		\Plus{}_i	& \Imaginary{}		& \textrm{i}\Imaginary{}
	\end{bmatrix}	$
	%
	$\begin{bmatrix}
		\Minus{}_i	& 0		& 0 \\
		\Plus{}_i	& \Imaginary{}	& \textrm{i}\Imaginary{} \\
		\Plus{}_i	&  \Real{}& \textrm{i}\Real{} \\
	\end{bmatrix}$ \\

@@

		\textrm{i}\Real{}	& \Plus{}_r		& \Real{} \\
		0				& \Minus{}_r	& 0 \\
		\textrm{i}\Imaginary{}	& \Plus{}_r		& \Imaginary{}
	\end{bmatrix}$
	%
	$\begin{bmatrix}
		\textrm{i}\Imaginary{}	& \Plus{}_r		&  \Imaginary{} \\
		0				& \Minus{}_r	& 0 \\
		\textrm{i}\Real{}	& \Plus{}_r		& \Real{} \\
	\end{bmatrix}$
	%
	$\begin{bmatrix}
		\Real{}	&\Plus{}_r		&   \textrm{i}\Real{} \\
		0		& \Minus{}_r	&  0 \\
		\Imaginary{}	&\Plus{}_r		& \textrm{i}\Imaginary{}
	\end{bmatrix}	$ 
	%
	$\begin{bmatrix}
		\Imaginary{}	& \Plus{}_r	& \textrm{i}\Imaginary{} \\
		0		&\Minus{}_r	&  0 \\
		\Real{}	& \Plus{}_r	&  \textrm{i}\Real{} \\
	\end{bmatrix}$ \\

@@

	$\begin{bmatrix}
		\textrm{i}\Real{}	& \Plus{}_i		& \Real{} \\
		0				& \Minus{}_i	& 0 \\
		\textrm{i}\Imaginary{}	& \Plus{}_i		& \Imaginary{}
	\end{bmatrix}$
	%
	$\begin{bmatrix}
		\textrm{i}\Imaginary{}	& \Plus{}_i		&  \Imaginary{} \\
		0				& \Minus{}_i	& 0 \\
		\textrm{i}\Real{}	& \Plus{}_i	& \Real{} \\
	\end{bmatrix}$ 
	%
	$\begin{bmatrix}
		\Real{}	&\Plus{}_i		&   \textrm{i}\Real{} \\
		0		& \Minus{}_i	&  0 \\
		\Imaginary{}	&\Plus{}_i		& \textrm{i}\Imaginary{}
	\end{bmatrix}	$ 
	%
	$\begin{bmatrix}
		\Imaginary{}	& \Plus{}_i	& \textrm{i}\Imaginary{} \\
		0		&\Minus{}_i	&  0 \\
		\Real{}	& \Plus{}_i	&  \textrm{i}\Real{} \\
	\end{bmatrix}$ \\

@@

\subsection{Example C++ implementation}

\begin{verbatim}
static std::complex<double> c3_Minus_Real(std::complex<double>& a) {
   const std::complex<double> c = { -a.real(), -a.real() + a.imag() };
   return c;
}

C3 C3::c3_s1(const C3& a) {
   C3 c;
   c[0] = c3_Minus_Real(a[0]);
   c[1] = c3_Plus_Real(a[0]) + c3_Real(a[1]) +
   c3_I_Times_Real(a[2]);
   c[2] = c3_Plus_Real(a[0]) + c3_Imag(a[1]) +
   c3_I_Times_Imag(a[2]);
   return c;
}
\end{verbatim}

@@

The matrix multiplication can be implemented as follows (including
only one example of the functions for operators (c3\_Minus\_Real))"

Therefore, RedMat = \\
\begin{center}
	$\begin{bmatrix}
		\Minus{}_r	& 0			& 0 \\
		\Plus{}_r	&  \textrm{i}\Real{}	& \Real{} \\
		\Plus{}_r	& \textrm{i}\Imaginary{}		&\Imaginary{}
	\end{bmatrix}	$
\end{center}

@@

\begin{center}
	\{(-1.000,1.000) (4.000,6.000) (5.000,7.000)\} =\\
	$\begin{bmatrix}
		\Minus{}_r	& 0			& 0 \\
\Plus{}_r	&  \textrm{i}\Real{}	& \Real{} \\
\Plus{}_r	& \textrm{i}\Imaginary{}		&\Imaginary{}
	\end{bmatrix}	$
	$\begin{Bmatrix}
		(1,2)\\
		(3,4)\\
		(5,6)
	\end{Bmatrix}$\\

@@

	The identity in \CIII{} could also be written:\\

	$\bf{c'}$  = 
	$\begin{bmatrix}
		$1$	& $0$						&  $0$ \\
		$0$	& \Real{} +\textrm{i}\Imaginary{}	& $0$ \\
		$0$	& $0$						& \Real{} +\textrm{i}\Imaginary{} \\
	\end{bmatrix}$ 
	$\bf{c}$.
	\\
	which is simply replacement of the value one with an
	equivalent representation as operators.

@@

\begin{figure}
	\includegraphics[width=1.0\textwidth]{19_52}
	\label{19_57}
	\caption{The PLA2 unit cells, Niggli-reduced, and five copies were perturbed 10\%
		orthogonally to \SVI{} vector, followed by Niggli reduction.}
\end{figure}
